A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-05 paper.tex
Cite MQTT
Fix grammar

Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristic of distributed ledgers, which reduce the risks of centralized storage services. Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegate MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

\subsubsection{Infrastructure}
To build the system, MQTT is chosen as the communication protocol. MQTT protocol utilizes much more lightweight packet than HTTP protocol has. The topic-based publish-subscribe pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on low-level edge devices with limited bandwidth. The publish-subscribe model decouples publishers and subscribers in many ways:

>>>>

Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services. Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

\subsubsection{Infrastructure}
To build the system, MQTT\cite{MQTT} is chosen as the communication protocol. MQTT protocol utilizes much more lightweight packet than HTTP protocol has. The topic-based publish-subscribe pattern and lightweight packet that MQTT adopts would undoubtedly play an important role on low-level edge devices with limited bandwidth. The publish-subscribe model decouples publishers and subscribers in many ways:
